---
title: "TASK"
author: "Stuti Subramani"
date: "2022-07-13"
output:
  word_document: default
  html_document: default
---

## TASK1- PREDICTION USING SUPERVISED ML
### Objective- To predict the marks obtained by the students based on the number of hours they study.
Dataset: http://bit.ly/w-data

#### IMPORTING REQUIRED LIBRARIES
```{r}
library(readr)
library(ggplot2)
```  

#### IMPORTING AND READING THE DATA
```{r}
internship_data <- read_csv("https://raw.githubusercontent.com/AdiPersonalWorks/Random/master/student_scores%20-%20student_scores.csv")
View(internship_data)
```


#### VISUALIZING THE DATA
```{r}
ggplot(internship_data) + geom_point(mapping= aes(x=Hours,y=Scores)) +labs(title ="Number of hours studied vs percentage of marks", caption= "There is a positive linear relation between the number of hours studied and percentage of marks obtained by a student.")
```


#### APPLYING LINEAR REGRESSION
```{r}
model= lm(internship_data$Scores~internship_data$Hours)
summary(model)
```


#### PLOTTING A REGRESSION LINE

```{r}
ggplot(internship_data, aes(x=Hours,y=Scores)) + geom_point() +stat_smooth(method="lm",col="dodgerblue3") +labs(title= "Linear Model fitted tothe given data")
```


#### PREDICTING THE SCORES
```{r}
predicted_scores= predict(model,data.frame(internship_data$Hours))
```


#### COMPARING ACTUAL V/S PREDICTED
```{r}
data.frame(predicted_scores,internship_data$Scores)
```


#### WHAT WILL BE THE PREDICTED SCORE IF THE STUDENT STUDIES 9.25 HOURS A DAY?
```{r}
Hours=9.25
Score= model$coefficients[1]+ model$coefficients[2]*Hours
Score
```
According to the Regression model if the student studies for 9.25 hours a day then he/she is likely to score 92.9 marks.


#### EVALUATING THE MODEL
```{r}
summary(model)$r.squared
```
##### The R square value is 0.95. Therefore, the model has worked well for our data.

